On X-ray emission from Fast Blue Optical Transients

### 2023-05-10 papers/FBOTcompton/fbotcompton.tex
paper

For hydrodinamcal simulation we use code PLUTO \cite{MignonePluto}. We used several nested setups on different scales. At first we performed 3d modeling of two stable stars with parameters described above until they winds form a stable configuration. First star is placed at point with coordinates $x_1 = 0, y_1 = 0, z_1 = 0$, and the second at point with $x_2 = 0, y_2 = 0, z_2 = 1.4\cdot10^{17} cm$. Plane x-y is equatorial plane of winds of both stars. Sizes of the simulation box are $Lx = 6\cdot 10^{17} cm$ and $Ly = Lz = 3\cdot 10^{17}$ with number of grid points 400, 200 and 200 respectively. The next step was 1d spherical modeling of second star explosion. We use ejecta mass $M_{ej} = 0.1 M_\odot$ and velocity $v_{ej} = 0.3 c$ and initial conditions as described in \cite{}. At the third step we simulated setup with smaller scale - with size $Lx = 1.05\cdot 10^{17} cm$ and $Ly = Lz = 0.9\cdot 10^{16}$ and combined results of the previous steps as initial conditions. Also results of 1d modeling were used as time-dependent boundary condition on the right boundary. And at the last step, in setup with the smallest scale $Lx = 0.3\cdot 10^{17} cm$ and $Ly = Lz = 1.5\cdot 10^{15}$, wich is necessary to resolve bow- and tremination shock of the wind of the first star, we use results of the third step as initial and boundary conditions. Number density in different setups and their ierarchy scheme is shown on figure \ref{density}. On the panel a one can see iteraction of two winds in large-scale simulation at time before the explosion. On the panel b propagation of ejecta in middle-scale simulation at time $t_1 \approx 1.0\cdot10^7 s$ is shown. On the panel c one can see it in small-scale simulation at time $t_2 \approx 1.1\cdot10^7 s$. Ans on the panel d there is zoomed picture of wind bowshock in small-scale simulation at time $t_3 \approx 1.4\cdot10^7 s$ Magnetic field at the same time moments is shown on figure \ref{Bfield}.
\begin{figure}
	\centering
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{./fig/density.png} 
		\caption{Density profile of the system at different time moments}
		\label{density}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{./fig/Bfield.png} 
		\caption{Magnetic field profile of the system at different time moments}
		\label{Bfield}
	\end{minipage}
\end{figure}

Simulations showed that ejecta of supernovae, moving in interstellar medium has profile with thin and dense peak, with parameters number density $n \approx 10^5$ and width $d = 10^{15}$.

The wind shock has radius $R_w \approx 0.5\times10^{14} cm$ and number density $n_w \approx 10^9 cm^{-3}$. With this parameters, and luminocity and temperature of the star, one can estimate observed X-ray flux, produxed by inverse compton scattering.

>>>>

For hydrodinamcal simulation we use code PLUTO \cite{MignonePluto}. We used several nested setups on different scales. At first we performed 3d modeling of two stable stars with parameters described above until they winds form a stable configuration. First star is placed at point with coordinates $x_1 = 0, y_1 = 0, z_1 = 0$, and the second at point with $x_2 = 0, y_2 = 0, z_2 = 1.4\cdot10^{17} cm$. Plane x-y is equatorial plane of winds of both stars. Sizes of the simulation box are $Lx = 6\cdot 10^{17} cm$ and $Ly = Lz = 3\cdot 10^{17}$ with number of grid points 400, 200 and 200 respectively. The next step was 1d spherical modeling of second star explosion. We use ejecta mass $M_{ej} = 0.1 M_\odot$ and velocity $v_{ej} = 0.3 c$ and initial conditions as described in \cite{Chevalier1982, Petruk2021snr}. The simulation box is splitted into three regions - in the central region with radius $r_0 = ?$ density is constant and velocity is proportional to radius $v(r) = 0.3 c r/r_0$. In the next region between $r_0$ and $r_1 = 2 r_0$ number density depends on radius as $n(r) \propto r^{-9}$ and velocity is also proportional to radius. And in the last region with $r > r_1$ stellar wind with constant velocity $v_w$ and mass loss $\dot{M}$is initialized. Profiles of ejecta density at different time moments are shown on figure \ref{snr}.
\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{./fig/snr.png} 
	\caption{Density profile of supernova explosion.}
	\label{snr}
\end{figure}

At the third step we simulated setup with smaller scale - with size $Lx = 1.05\cdot 10^{17} cm$ and $Ly = Lz = 0.9\cdot 10^{16}$ and combined results of the previous steps as initial conditions. Also results of 1d modeling were used as time-dependent boundary condition on the right boundary. And at the last step, in setup with the smallest scale $Lx = 0.3\cdot 10^{17} cm$ and $Ly = Lz = 1.5\cdot 10^{15}$, which is necessary to resolve bow- and tremination shock of the wind of the first star, we use results of the third step as initial and boundary conditions. Number density in different setups and their ierarchy scheme is shown on figure \ref{density}. On the panel a one can see iteraction of two winds in large-scale simulation at time before the explosion. On the panel b propagation of ejecta in middle-scale simulation at time $t_1 \approx 1.0\cdot10^7 s$ is shown. On the panel c one can see it in small-scale simulation at time $t_2 \approx 1.1\cdot10^7 s$. Ans on the panel d there is zoomed picture of wind bowshock in small-scale simulation at time $t_3 \approx 1.4\cdot10^7 s$ Magnetic field at the same time moments is shown on figure \ref{Bfield}.
\begin{figure}
	\centering
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{./fig/density.png} 
		\caption{Density profile of the system at different time moments}
		\label{density}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{./fig/Bfield.png} 
		\caption{Magnetic field profile of the system at different time moments}
		\label{Bfield}
	\end{minipage}
\end{figure}

Simulations showed that ejecta of supernovae, moving in interstellar medium has profile with thin and dense peak with number density $n \approx 10^5 cm^{-3}$ and width $d = 10^{16}$, and wide region with number density $\approx 10^4 cm^{-3}$ behind the peak.

The wind bow-shock has radius $R_w \approx 2\times10^{14} cm$ and number density $n_w \approx 10^9 cm^{-3}$. With this parameters, and luminocity and temperature of the star, one can estimate observed X-ray flux, produced by inverse compton scattering.
